Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-03-19 RR_manuscript/Draft_RR.Rmd
:memo: - analytical > analytic; remove todo tex package

---
title             : "Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech."
shorttitle        : "Many analysts - one speech data set"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
output:
  bookdown::pdf_document2:
    number_sections: true
    latex_engine: xelatex
    keep_tex: true
geometry: margin=4cm
fontsize: 12pt
indent: true
header-includes:
  - \usepackage{cleveref}
  - \setlength{\marginparwidth}{2cm}
  - \usepackage[todonotes={textsize=tiny}]{changes}
  - \definechangesauthor[name={Stefano Coretta}, color=red]{SC}
  - \definechangesauthor[name={Timo Röttger}, color=blue]{TR}
  - \definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
---

@@

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
<!-- TODO: add REFS about variable conclusions from reliable data -->
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

@@

Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision making procedure to apply.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured [@roettger2019researcher].
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility [e.g. @miguel2014promoting; @klein2018practical] and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare [@wicherts2006poor].

Analytical flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g. @wicherts2016, Charles et al. 2019, @roettger2019researcher], notwithstanding, there are still many unknowns regarding the extent of analytical plurality in practice.
<!-- TODO: add REFS Charles et al. 2019 -->
Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
<!-- NOTE: (?) I think this should be part of the previous paragraph. -->

@@

In a collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
Analytical approaches and consequently the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
Out of the 29 analytical strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise nor bias.

Several other recent studies corroborated this analytical flexibility across different disciplines.
Both @dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
<!-- TODO: Parker et al. (ECO) REFS -->
Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also Parker et al. (accepted) on analytical flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
@bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
Results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.

While these studies attested a large degree of analytical flexibility with possibly impactful consequences, they only investigated analytical decisions related to inferential statistics or the architecture of computational models.
In these studies the data sets were fixed and neither data collection nor measurement could be changed.
However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.

For instance, @flake2020 discuss the cascading impact that different practices can have on psychometric research.
The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
Taken together, these aspects alone exponentially increase the combinations of possible analytical choices, and hence flexibility in research outcomes.

In social sciences concerned with communication, human behavior is sometimes measured as a complex visual or acoustic signal.
This added complexity introduces further fork junctions in the research pipe-line, and in turn further increases analytical flexibility.
The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.

@@

Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision.
Take for example the following sentence in (1).

@@

When looking at phrase-level temporal domains, the number of possible analytical pipelines increases exponentially.
This plurality of analytical paths is illustrated in Figure \@ref(fig:forkingPaths).
Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
For example, we could measure f0 at specific points in time like the onset of the window, the offset, or the midpoint.
We could also measure the value or time of the minimum or maximum f0 value.
We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data [see @gordon2017acoustic].
And the garden of forking paths does not stop here.
<!-- TODO: add examples of pitch tracking options -->
Figure \@ref(fig:forkingPaths), illustrates a specific option to automatically calculate f0.
Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
<!-- NOTE: (JVC) Im having a bit of trouble with this sentence. I tried to fix it and now I am realizing I don't quite follow (JVC) -->

<!-- FIGURE -->
(ref:forkingPaths) Illustrations of the analytical flexibility associated with acoustic analyses. (A) an example of multiple possible and justifiable decisions when comparing two utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b. The words "another is highlighted by the green box"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.

@@

These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e. after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytical flexibility when choosing measures and operationalizing underlying theoretical constructs.
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we will provide analytical teams with an experimentally elicited speech production data set.
The study aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
In the following, we will shortly introduce the research question of the original study.

@@

As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytical choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytical flexibility that social science might face across disciplines.
We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.

@@

<!-- TODO: project timeline -->
We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take \highlight{XX months (Table X).}
The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.

@@

<!-- TODO: Parker et al. (ECO) REFS -->
Following Parker et al. \highlight{[ECO RR]}, we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient.
The probability $Pr$ that a CrI interval does not include 0 is obtained via the *t*-statistic:

@@

<!-- TODO: add LINK to analytical survey -->
Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytical choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

### Meta-analytical estimation {#s:meta-est}

<!-- NOTE: (SC) t would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model -->
We will summarize the variability in reported effect sizes using Bayesian meta-analytic techniques.
Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Factor-level ordering for each categorical variable will mirror that of the original analyses.
Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

@@

After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, we will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model.
The outcome variable will be the set of standardized effect sizes $\eta_i$.
The likelihood of $\eta_i$ is assumed to correspond to a normal distribution [@knight2000].
The analysis teams will be entered as a group-level effect (i.e., random effect, `(1 | team)`).
The standard errors $\text{se}_i$ will be included as the standard deviation $\sigma_i$ of $\eta_i$ to fit a measurement-error model, as discussed above.
We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\alpha_{\text{t}[i]}$ ($HalfCauchy(0, 1)$).
We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions.
The analysis will be conducted in R [@R-base] and fit using Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017].
<!-- TODO: add LINK to code of the meta-analytical model -->
The code used to run the model can be found here: INSERT LINK.

@@

<!-- NOTE: I keep changing meta-analytical to meta-analytic (the -cal sounds weird to me). My unscientific google searching shows that people use both, but meta-analytic is much more common (nearly 4 million hits vs. 500k) -->
<!-- NOTE: (SC) I tend to use analytical to mean "related to analysis" and "analytic" in opposition to "synthetic" (from their use in logic and linguistics) but I am flex as long as we are consistent. -->

@@

```{r funnel-calc, include=FALSE, eval=FALSE}
# meta_bm is the meta-analytical Bayesian regression model
meta_bm_est <- fixef(meta_bm)["Intercept","Estimate"]
meta_bm_q2.5 <- fixef(meta_bm)["Intercept","Q2.5"]
meta_bm_q97.5 <- fixef(meta_bm)["Intercept","Q97.5"]

@@

### Analytical and demographic predictors affecting effect sizes {#ana-factors}
<!-- NOTE: (TR) I think we should use the term predictors. Factors is really ambiguous -->
As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and researcher-related factors.

**Analytical predictors**. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:

>>>>

---
title             : "Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech."
shorttitle        : "Many analysts - one speech data set"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
output:
  bookdown::pdf_document2:
    number_sections: true
    latex_engine: xelatex
    keep_tex: true
geometry: margin=4cm
fontsize: 12pt
indent: true
header-includes:
  - \usepackage{cleveref}
---

@@

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
<!-- TODO: add REFS about variable conclusions from reliable data -->
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

@@

Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision making procedure to apply.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytic pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured [@roettger2019researcher].
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility [e.g. @miguel2014promoting; @klein2018practical] and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare [@wicherts2006poor].

Analytic flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g. @wicherts2016, Charles et al. 2019, @roettger2019researcher], notwithstanding, there are still many unknowns regarding the extent of analytic plurality in practice.
<!-- TODO: add REFS Charles et al. 2019 -->
Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
<!-- NOTE: (?) I think this should be part of the previous paragraph. -->

@@

In a collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
Analytic approaches and consequently the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
Out of the 29 analytic strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise nor bias.

Several other recent studies corroborated this analytic flexibility across different disciplines.
Both @dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
<!-- TODO: Parker et al. (ECO) REFS -->
Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also Parker et al. (accepted) on analytic flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
@bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
Results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.

While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they only investigated analytic decisions related to inferential statistics or the architecture of computational models.
In these studies the data sets were fixed and neither data collection nor measurement could be changed.
However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.

For instance, @flake2020 discuss the cascading impact that different practices can have on psychometric research.
The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
Taken together, these aspects alone exponentially increase the combinations of possible analytic choices, and hence flexibility in research outcomes.

In social sciences concerned with communication, human behavior is sometimes measured as a complex visual or acoustic signal.
This added complexity introduces further fork junctions in the research pipe-line, and in turn further increases analytic flexibility.
The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.

@@

Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytic decision.
Take for example the following sentence in (1).

@@

When looking at phrase-level temporal domains, the number of possible analytic pipelines increases exponentially.
This plurality of analytic paths is illustrated in Figure \@ref(fig:forkingPaths).
Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
For example, we could measure f0 at specific points in time like the onset of the window, the offset, or the midpoint.
We could also measure the value or time of the minimum or maximum f0 value.
We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data [see @gordon2017acoustic].
And the garden of forking paths does not stop here.
<!-- TODO: add examples of pitch tracking options -->
Figure \@ref(fig:forkingPaths), illustrates a specific option to automatically calculate f0.
Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
<!-- NOTE: (JVC) Im having a bit of trouble with this sentence. I tried to fix it and now I am realizing I don't quite follow (JVC) -->

<!-- FIGURE -->
(ref:forkingPaths) Illustrations of the analytic flexibility associated with acoustic analyses. (A) an example of multiple possible and justifiable decisions when comparing two utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b. The words "another is highlighted by the green box"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.

@@

These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e. after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytic flexibility when choosing measures and operationalizing underlying theoretical constructs.
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we will provide analytic teams with an experimentally elicited speech production data set.
The study aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
In the following, we will shortly introduce the research question of the original study.

@@

As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.

@@

<!-- TODO: project timeline -->
We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take XX months (Table X).
The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.

@@

<!-- TODO: Parker et al. (ECO) REFS -->
Following Parker et al. [ECO RR], we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient.
The probability $Pr$ that a CrI interval does not include 0 is obtained via the *t*-statistic:

@@

<!-- TODO: add LINK to analytic survey -->
Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

### Meta-analytic estimation {#s:meta-est}

<!-- NOTE: (SC) t would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytic model -->
We will summarize the variability in reported effect sizes using Bayesian meta-analytic techniques.
Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Factor-level ordering for each categorical variable will mirror that of the original analyses.
Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

@@

After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, we will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model.
The outcome variable will be the set of standardized effect sizes $\eta_i$.
The likelihood of $\eta_i$ is assumed to correspond to a normal distribution [@knight2000].
The analysis teams will be entered as a group-level effect (i.e., random effect, `(1 | team)`).
The standard errors $\text{se}_i$ will be included as the standard deviation $\sigma_i$ of $\eta_i$ to fit a measurement-error model, as discussed above.
We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\alpha_{\text{t}[i]}$ ($HalfCauchy(0, 1)$).
We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions.
The analysis will be conducted in R [@R-base] and fit using Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017].
<!-- TODO: add LINK to code of the meta-analytic model -->
The code used to run the model can be found here: INSERT LINK.

@@

<!-- NOTE: I keep changing meta-analytic to meta-analytic (the -cal sounds weird to me). My unscientific google searching shows that people use both, but meta-analytic is much more common (nearly 4 million hits vs. 500k) -->
<!-- NOTE: (SC) I tend to use analytic to mean "related to analysis" and "analytic" in opposition to "synthetic" (from their use in logic and linguistics) but I am flex as long as we are consistent. -->

@@

```{r funnel-calc, include=FALSE, eval=FALSE}
# meta_bm is the meta-analytic Bayesian regression model
meta_bm_est <- fixef(meta_bm)["Intercept","Estimate"]
meta_bm_q2.5 <- fixef(meta_bm)["Intercept","Q2.5"]
meta_bm_q97.5 <- fixef(meta_bm)["Intercept","Q97.5"]

@@

### Analytic and demographic predictors affecting effect sizes {#ana-factors}
<!-- NOTE: (TR) I think we should use the term predictors. Factors is really ambiguous -->
As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytic and researcher-related factors.

**Analytic predictors**. We will estimate the influence of the following predictors related to the analytic characteristics of each team's reported analysis:
